Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2023-09-18 Paper/Supplementary.tex
Adding variable names

$\atan(y,x)$ & -- & -- & The four quadrant inverse tangent which returns values in the interval $[-\pi,\pi]$ , inclusive.\\
$\cw$ & c & $m s^{-1}$ & Sound speed in water.\\
$\decfac(\stagesym)$ & filter\_v[n]['D'] & 1 & Integer filter decimation factor.\\
$\dft_\ndft(x)$ & N\_DFT & -- & The discrete Fourier transform of length $\ndft$ of $x$.\\
$\freqsym$ & & Hz & Frequency.\\
$\fc$ & & Hz & Frequency at centre of linear upsweep chirp pulse. Equivalent to $\fstart + \frac{|\fstop - \fstart|}{2}$.\\
$\fn$ & f\_n & Hz & Nominal operating frequency of a transducer.\\
$\fs$ & f\_s & Hz & Analogue to digital sampling frequency.\\
$\fsdec$ & f\_s\_dec & Hz & Decimated sampling frequency.\\
$\fstart$ & f\_1 & Hz & Start frequency of linear upsweep chirp pulse.\\
$\fstop$ & f\_2 & Hz & Stop frequency of linear upsweep chirp pulse.\\

$\gain(\along,\athw,\freqsym)$ & g\_theta\_phi\_m & 1 & Transducer gain as a function of echo arrival angle in the beam and frequency.\\

@@

$\gainzero(\freqsym)$ & g\_0\_m & 1 & Transducer gain along the main acoustic axis, i.e. $\gain(\along, \athw,\freqsym)$ where $\along = \athw = 0$.\\

$\hbp(\genidxsym,\stagesym)$ & filter\_v[n]['h\_fl\_i'] & 1 & Complex valued receiving filter coefficients.\\
$\genidxsym$ & & 1 & Generic integer index.\\
$\Im(x)$ & & -- & The imaginary part of $x$.\\
$j$ & & & The square root of $-1$.\\
$\samplesymf$ & m & 1 & Sample index in frequency domain.\\

$\nchannels$ & N\_u & 1 & Total number of transducer sectors/transceiver channels that are used to receive and process the acoustic signal.\\
$\nstages$ & & 1 & Total number of filter stages.\\
$\nw$ & & 1 & Number of samples used in the sliding Hanning window.\\
$\samplesymt$ & n & 1 & Sample index in time domain.\\

$\prxetf(\freqsym)$ &  & W & FT of the received electric power in a matched load for the signal from a single target at frequency $\freqsym$.\\
$\prxetf(\samplesymf)$ & P\_rx\_e\_t\_m & W & DFT of the received electric power in a matched load for the signal from a single target.\\
$\prxevf(\freqsym)$ & & W & FT of the received electric power in a matched load for the signal from a volume at frequency $\freqsym$.\\
$\prxevf(\samplesymf)$ & P\_rx\_e\_v\_m & W$\textrm{m}^2$ & DFT of the received electric power in a matched load for the signal from a volume.\\
$\prxe(\samplesymt)$  & p\_rx\_e\_n & W & Received electric power in a matched load.\\

$\ptxe$ & p\_tx\_e & W & Transmitted electric power.\\
$\ptxauto(\samplesymt)$ & p\_tx\_auto & 1 & Square of the absolute value of the matched filter autocorrelation function.\\

$\Re(x)$ & & -- & The real part of $x$.\\
$\range$ & & m & Distance from transducer.\\
$\rangeref$ & & m & Reference distance. \\
$\range_c$ & & m & Distance from the transducer to the centre of the range volume covered by $\tslide$.\\
$\range_c(\samplesymt)$ & & m & $range_c$ at sample number $\samplesymt$.\\
$\range(\samplesymt)$ & r\_n & m & Distance from transducer.\\

@@

$\hannw$ & & 1 & The Hann window function.\\
$\hannw(\genidxsym)$ & & 1 & The Hann window function for index i, defined by $w(i) = 0.5(1+\cos (2\pi i /N_w)), -N_w/2 \leq i \leq N_w/2$.\\
$\hannwnorm(\genidxsym)$ & & 1 & Normalised Hann window.\\

@@

$\ymfautof(\samplesymf)$ & & 1 & Discrete Fourier transform (DFT) of the autocorrelation function for the matched filter.\\
$\ymfautoredf(\samplesymf)$ &  & 1 & DFT of the reduced autocorrelation function for the matched filter.\\
$\ypctargetf(\samplesymf)$ & & V & DFT of the pulse compressed signal from a single target.\\
$\ypctargetnormf(\samplesymf)$ & & Vm & DFT of the pulse compressed signal from a single target 
normalized by the DFT of the reduced autocorrelation function for the matched filter.\\
$\ypcvolumef(\samplesymf)$ & & Vm & DFT of the pulse compressed signal from a volume. Compensated for spreading loss.\\
$\ypcvolumenormf(\samplesymf)$ & & V & DFT of the pulse compressed signal from a single volume normalized by the DFT of the reduced autocorrelation function for the matched filter.  Compensated for spreading loss.\\

>>>>

$\atan(y,x)$ & -- & -- & The four quadrant inverse tangent which returns values in the interval $[-\pi,\pi]$ , inclusive.\\
$\cw$ & c & $m s^{-1}$ & Sound speed in water.\\
$\decfac(\stagesym)$ & \code{filter_v[n]['D']} & 1 & Integer filter decimation factor.\\
$\dft_\ndft(x)$ & & -- & The discrete Fourier transform of length $\ndft$ of $x$.\\
$\freqsym$ & & Hz & Frequency.\\
$\fc$ & & Hz & Frequency at centre of linear upsweep chirp pulse. Equivalent to $\fstart + \frac{|\fstop - \fstart|}{2}$.\\
$\fn$ & \code{f_n} & Hz & Nominal operating frequency of a transducer.\\
$\fs$ & \code{f_s} & Hz & Analogue to digital sampling frequency.\\
$\fsdec$ & \code{f_s_dec} & Hz & Decimated sampling frequency.\\
$\fstart$ & \code{f_1} & Hz & Start frequency of linear upsweep chirp pulse.\\
$\fstop$ & \code{f_2} & Hz & Stop frequency of linear upsweep chirp pulse.\\

$\gain(\along,\athw,\freqsym)$ & \code{g_theta_phi_m} & 1 & Transducer gain as a function of echo arrival angle in the beam and frequency.\\

@@

$\gainzero(\freqsym)$ & \code{g_0_m} & 1 & Transducer gain along the main acoustic axis, i.e. $\gain(\along, \athw,\freqsym)$ where $\along = \athw = 0$.\\

$\hbp(\genidxsym,\stagesym)$ & \code{filter_v[n]['h_fl_i']} & 1 & Complex valued receiving filter coefficients.\\
$\genidxsym$ & & 1 & Generic integer index.\\
$\Im(x)$ & & -- & The imaginary part of $x$.\\
$j$ & & & The square root of $-1$.\\
$\samplesymf$ & \code{m} & 1 & Sample index in frequency domain.\\

$\nchannels$ & \code{N_u} & 1 & Total number of transducer sectors/transceiver channels that are used to receive and process the acoustic signal.\\
$\nstages$ & & 1 & Total number of filter stages.\\
$\nw$ & & 1 & Number of samples used in the sliding Hanning window.\\
$\samplesymt$ & n & 1 & Sample index in time domain.\\

$\prxetf(\freqsym)$ &  & W & FT of the received electric power in a matched load for the signal from a single target at frequency $\freqsym$.\\
$\prxetf(\samplesymf)$ & \code{P_rx_e_t_m} & W & DFT of the received electric power in a matched load for the signal from a single target.\\
$\prxevf(\freqsym)$ & & W & FT of the received electric power in a matched load for the signal from a volume at frequency $\freqsym$.\\
$\prxevf(\samplesymf)$ & \code{P_rx_e_v_m} & W$\textrm{m}^2$ & DFT of the received electric power in a matched load for the signal from a volume.\\
$\prxe(\samplesymt)$  & \code{p_rx_e_n} & W & Received electric power in a matched load.\\

$\ptxe$ & \code{p_tx_e} & W & Transmitted electric power.\\
$\ptxauto(\samplesymt)$ & \code{p_tx_auto} & 1 & Square of the absolute value of the matched filter autocorrelation function.\\

$\Re(x)$ & & -- & The real part of $x$.\\
$\range$ & & m & Distance from transducer.\\
$\rangeref$ & & m & Reference distance. \\
$\range_c$ & & m & Distance from the transducer to the centre of the range volume covered by $\tslide$.\\
$\range_c(\samplesymt)$ & & m & $range_c$ at sample number $\samplesymt$.\\
$\range(\samplesymt)$ & \code{r_n} & m & Distance from transducer.\\

@@

$\hannw$ & & 1 & The Hann window function.\\
$\hannw(\genidxsym)$ & w\_i & 1 & The Hann window function for index i, defined by $w(i) = 0.5(1+\cos (2\pi i /N_w)), -N_w/2 \leq i \leq N_w/2$.\\
$\hannwnorm(\genidxsym)$ & w\_tilde\_i & 1 & Normalised Hann window.\\

@@

$\ymfautof(\samplesymf)$ & Y\_mf\_auto\_m & 1 & Discrete Fourier transform (DFT) of the autocorrelation function for the matched filter.\\
$\ymfautoredf(\samplesymf)$ & Y\_mf\_auto\_m\_red & 1 & DFT of the reduced autocorrelation function for the matched filter.\\
$\ypctargetf(\samplesymf)$ & Y\_pc\_t\_m & V & DFT of the pulse compressed signal from a single target.\\
$\ypctargetnormf(\samplesymf)$ & Y\_tilde\_pc\_t\_m & Vm & DFT of the pulse compressed signal from a single target 
normalized by the DFT of the reduced autocorrelation function for the matched filter.\\
$\ypcvolumef(\samplesymf)$ & Y\_pc\_v\_m & Vm & DFT of the pulse compressed signal from a volume. Compensated for spreading loss.\\
$\ypcvolumenormf(\samplesymf)$ & \code{Y\_tilde\_pc\_v\_m} & V & DFT of the pulse compressed signal from a single volume normalized by the DFT of the reduced autocorrelation function for the matched filter.  Compensated for spreading loss.\\
